Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-24 paper/paper.tex
Update task granularity plot/text

Figure~\ref{fig:stretching} shows the relative performance of the algorithms as the scaling factor is increased from 1 to 16. Each data point represents the result of 500 simulations (5 random seeds for 10 budgets and 10 deadlines). The best scores percent was calculated the same way as it was for Figure~\ref{fig:distributions}.

The figure clearly shows that, as the scaling factor increases, the relative performance of SPSS increases as well. In all cases, the performance of SPSS is superior to the dynamic algorithms for scaling factors greater than about 8. This suggests that, in general, for fine-grained workflows, the dynamic algorithms will produce better scores, and for coarse-grained workflows SPSS will produce better scores.

\begin{figure*}[p]
    \centering
    \subfloat[CyberShake]{
        \includegraphics[width=0.75\textwidth]{stretching_cybershake}
    }\\
    \subfloat[Montage]{
        \includegraphics[width=0.75\textwidth]{stretching_montage}
    }
    \caption[Percentage of high scores achieved by each algorithm for Montage and Cybershake ensembles when task runtime is stretched]{Percentage of high scores achieved by each algorithm for Montage and Cybershake ensembles when task runtime is stretched. A stretching factor of $x$ means that the runtime of tasks in each workflow was multiplied by $x$.}
    \label{fig:stretching}
\end{figure*}

>>>>

Figure~\ref{fig:stretching} shows the relative performance of the algorithms as the scaling factor is increased from 1 to 16. This figure only shows results for the CyberShake application with pareto unsorted ensembles, but similar results were found for other ensemble types for both Montage and CyberShake. Each data point in the figure represents the result of 500 simulations (5 random seeds for 10 budgets and 10 deadlines). The best scores percent was calculated the same way as it was for Figure~\ref{fig:distributions}.

The figure shows that, as the scaling factor increases, the relative performance of SPSS increases as well. In this case SPSS performance surpasses DPDS and WA-DPDS for scaling factors larger than 2. In all other cases (other ensemble types for both applications), the performance of SPSS is superior to the dynamic algorithms for scaling factors greater than about 8. This suggests that, in general, for fine-grained workflows the dynamic algorithms will produce better scores, and for coarse-grained workflows SPSS will produce better scores.

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.4\textwidth]{stretching_cybershake}
    \caption[Percentage of high scores achieved by each algorithm for Cybershake pareto unsorted ensembles when task runtime is stretched]{Percentage of high scores achieved by each algorithm for Cybershake pareto unsorted ensembles when task runtime is stretched. A stretching factor of $x$ means that the runtime of tasks in each workflow was multiplied by $x$.}
    \label{fig:stretching}
\end{figure}
